---
title: "Errors in Hypothesis testing"
runtime: shiny
output: html_document
---

When performing a hypothesis test, there are a number of possible outcomes based on our null and alternative hypotheses.

Let's say we know absolutely that the null hypothesis is true. This would, of course, make the hypothesis test completely unnecessary. But let's think this through. If $H_0$ is true, and we reject the null, we have concluded incorrectly. We call this a "type 1 error." It is also known as "$\alpha$" or "significance level." But if $H_0$ is true and we fail to reject the null (FTR for short), then we have made the correct decision. We don't have a name for this.

On the other hand, if we know absolutely $H_a$ is true, then if we reject the null, we have come to the correct decision. We call this 'power.' But if $H_a$ is true and we fail to reject the null, we have again concluded incorrectly. But this is the opposite type of mistake. We call incorrectly failing to reject the null a "type 2 error," or '$\beta$.'


```{r, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



